rbcL community comparison

### 2019-11-02 code/rbcl_community_compare.Rmd
minor changes, make multi panel plot

# plot unifrac, colored by elevation
uf_plot <- ggplot(unifrac_plot_data, aes(x=NMDS2, y=NMDS1)) +
  geom_point(aes(color=elev_m), size=4) +
  scale_color_gradientn(colours = terrain.colors(8)[1:7]) +
  labs(color="Elevation (m)") +
  geom_text_repel(aes(label=alias))
uf_plot
```

@@

# check rel abund sums = 1
plot_data %>%
  group_by(alias) %>%
  summarise(sum(rel_abund))
```

@@

# order OTUs
otu_ord <- c("Chlainomonas A","Sanguina B", "Chloromonas spp. C","Chloromonas krienitzii D","Chloromonas muramotoi E","Chloromonas F", "Algae G","Chloromonas H", "Trebouxiophyceae I")

barplot <- ggplot(plot_data, aes(x=alias %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=otu_name), stat="identity") + # classic stacked relative abundance plot
  coord_flip() +
  facet_grid(~otu_name %>% fct_relevel(otu_ord), switch = "x") +
  labs( x="Sample ID") +
  cust_theme
barplot

@@

```{r combine, fig.width=7, fig.height=10}
combined_fig_3 <- grid.arrange(uf_plot, barplot, nrow=2)
```

@@

>>>>

# plot unifrac, colored by elevation
uf_plot <- ggplot(unifrac_plot_data, aes(x=NMDS2, y=NMDS1)) +
  geom_point(aes(color=elev_m), size=4) +
  scale_color_gradientn(colours = terrain.colors(8)[1:7]) +
  labs(color="Elevation (m)", tag="A") +
  geom_text_repel(aes(label=alias))
uf_plot
```

@@

# check rel abund sums ~= 1 (will be slightly higher, due to rounding)
plot_data %>%
  group_by(alias) %>%
  summarise(sum(rel_abund))
```

@@

otu_ord <- c("Chlainomonas A","Sanguina B", "Other Chloromonas","Chloromonas krienitzii","Chloromonas muramotoi C","Chloromonas D", "Algae E","Chloromonas F", "Trebouxiophyceae G")

barplot <- ggplot(plot_data, aes(x=alias %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=otu_name %>% fct_relevel(otu_ord)), stat="identity") + # classic stacked relative abundance plot
  coord_flip() +
  facet_grid(~otu_name %>% fct_relevel(otu_ord), switch = "x") +
  labs( x="Sample ID", tag="B") +
  cust_theme
barplot

@@

```{r combine, fig.width=7, fig.height=10}
combined_fig_3 <- gridExtra::grid.arrange(uf_plot, barplot, nrow=2)
```

@@

```{r}
faith_elev_plot <- ggplot(faiths, aes(y=PD, x=elev_m))+
  geom_point() +
  geom_smooth(method = "lm")+
  geom_text_repel(aes(label=alias))+
  labs(title="Phylogenetic diversity of snow algae rbcL vs elevation",y="Faith's phylogenetic diversity (PD)",x="Elevation (m)")
faith_elev_plot
```
